???

### 2018-05-12 inst/stable_line_proliferation/stable_line_proliferation.Rmd
adding stable line proliferation rds and raw processing script

---
title: "Figure 3c"
subtitle: "Monitoring growth of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

url <- fileMap(type = "rds")["Figure 3c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

---
title: "???"
subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

@@

data <- getData("Figure 3c")
